---
title: Predictors of NBA All-Start Status
author: Dan Flanagan, Lina Dimitrov, Sara Kim
output: html_document
---

```{r, set-chunk-opts, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r, here-i-am, include = FALSE}
here::i_am("report.Rmd")
```

```{r, set-up, include = FALSE}
data_clean <- readRDS(here::here("data/nba_data_clean.rds"))
table1 <- readRDS(here::here("output/table1.rds"))
table2 <- readRDS(here::here("output/table2.rds"))
table3 <- readRDS(here::here("output/table3.rds"))
figure1 <- readRDS(here::here("output/figure1.rds"))
figure2 <- readRDS(here::here("output/figure2.rds"))
pacman::p_load(dplyr, tidyr, ggplot2, zoo, gt, gtsummary)
```


## Project overview

This project investigates which player characteristics are predictive of being selected as an NBA All-Star among players who started at least 50% of their games played. We excluded players who played on multiple teams in the same season (traded). In this dataset, there were `r nrow(data_clean)` players.

## Descriptive analysis

Descriptive table based on All-Star status. 


```{r table1, fig.align="center", fig.width=6, fig.height=8, echo = FALSE}
table1

```

## Game performance (per 36 mins)

Comparison of game performance for All-Stars vs. Non-All-Stars, reveals that All-Stars score significantly more points compared to Non-All-Stars, per 36 minutes of playing time. Interestingly, All-Stars and Non-All-Stars have similar make percentages across all scoring categories: All field goals, 3-point shots, 2-point shots, and free throws. However, All-Stars take significantly more attempts in all scoring categories compared to Non-All-Stars, resulting in more points scored per 36 minutes.

```{r table2, fig.align="center", fig.width=6, fig.height=8, echo = FALSE}
table2

figure1
```

## Regression analysis

We ran a linear regression model regressing player characteristics on player All-Star status. 

```{r regression, fig.align="center", fig.width=10, fig.height=8, echo = FALSE, warning = FALSE, message = FALSE}
table3

figure2
```


